### 2018-04-11 paper/overview.tex
revised overview figures

% include code of running example and some figure:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.26\textwidth] %
    { \caption{\cc{dblAbs}: an example hierarchical program.} %
      \label{fig:multicall-code} }
    { \input{code/dblAbs.java} }
    %
    \ffigbox[.7\textwidth] %
    {\caption{$\mcchc$ as a directed hypergraph.
        % 
        Each relational predicate is depicted as a graph node
        while each clause is represented by a hyperedge.
        Each hyperedge is labelled by the fact in the corresponding CHC\@.
        Each node has a valid corresponding interpretation,
        written in braces.
      } %
      \label{fig:ex-graph} }
    % { \includegraphics[width=\linewidth]{fig/ex-deps.pdf} }
      {\input{fig/example}}
  \end{floatrow}
\end{figure}
% walk through code of running example:
%
\cc{dblAbs} is a small procedure that doubles the absolute value of
its input and stores the result in \cc{res}.
% state the safety problem:
The program also asserts that \cc{res} is greater than or equal to $0$
before exiting.
% talk about solving Horn Clauses:
Verifying this assertion reduces to solving a recursion-free
CHC system over a set of uninterpreted predicates that represent
the control locations in \cc{dblAbs}.
%
In particular, one such system $\mcchc$ is
%
\begin{align}
\label{chc}
  % semantic constraint of dbl:
\cc{dbl}(\cc{x}, \cc{d}) &\gets \cc{d} = 2 * \cc{x} \\
  % semantic constraint of line 3:
  \cc{L}_4(\cc{n}, \cc{abs}) &\gets  \cc{abs} = 0 \\
  % semantic constraint of line 5 (then branch)
  \cc{L}_6(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} \ge 0 \\
  % semantic constraint of line 6 (else branch)
  \cc{L}_8(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} < 0 \\
  % assign branch
  \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_6(\cc{n},\cc{abs}) \land \cc{abs'} = \cc{n} \\
   \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_8(\cc{n},\cc{abs}) \land \cc{abs'} = -\cc{n} \\
  % semantic constraint of main procedure:
   \cc{main}(\cc{n},\cc{res}) &\gets \cc{L}_9(\cc{n}, \cc{abs'}) \land
                                     \cc{dbl}(\cc{x}, \cc{d})
    \land \cc{abs'} = \cc{x} \land \cc{res} = \cc{d} \\
  %
    \bot &\gets \cc{main}(\cc{n}, \cc{res}) \land \cc{res} < 0 
\end{align}
%
While $\mcchc$ has been presented as the result
of a translation from \cc{dblAbs}, \sys is
purely a solver for CHC systems: it does not require access to the
concrete representation of a program, or for a given CHC system to be
the result of translation from a program at all.

@@

%% talk about expansion:
\begin{figure}
  \input{fig/hierarchy}
\end{figure}

>>>>

% include code of running example and some figure:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.3\textwidth] {%
      \caption{\cc{dblAbs}: an example hierarchical program.} %
      \label{fig:multicall-code} }
    {\lstinputlisting[
      basicstyle=\small,
      xleftmargin=\parindent,
      numbers=left,
      morekeywords={def, return, if, else, assert}]{code/dblAbs.java}
        % \input{code/dblAbs.java}}
    }
    %
    \ffigbox[.66\textwidth]{%
      \caption{A CHC system that models the safety condition of $\cc{dblAbs}$,
    named $\mcchc$.}}{%
      \label{fig:chc}
      \begin{align}
        % semantic constraint of dbl:
        \cc{dbl}(\cc{x}, \cc{d}) &\gets \cc{d} = 2 * \cc{x} \\
        % semantic constraint of line 3:
        \cc{L}_4(\cc{n}, \cc{abs}) &\gets  \cc{abs} = 0 \\
        % semantic constraint of line 5 (then branch)
        \cc{L}_6(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} \ge 0 \\
        % semantic constraint of line 6 (else branch)
        \cc{L}_8(\cc{n}, \cc{abs}) &\gets \cc{L}_4(\cc{n}, \cc{abs}) \land \cc{n} < 0 \\
        % assign branch
        \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_6(\cc{n},\cc{abs}) \land \cc{abs'} = \cc{n} \\
        \cc{L}_9(\cc{n}, \cc{abs'}) &\gets \cc{L}_8(\cc{n},\cc{abs}) \land \cc{abs'} = -\cc{n} \\
        % semantic constraint of main procedure:
        \cc{main}(\cc{n},\cc{res}) &\gets \cc{L}_9(\cc{n}, \cc{abs'}) \land
        \cc{dbl}(\cc{x}, \cc{d})
        \land \cc{abs'} = \cc{x} \land \cc{res} = \cc{d} \\
        %
        \bot &\gets \cc{main}(\cc{n}, \cc{res}) \land \cc{res} < 0 
      \end{align}
    }
  \end{floatrow}
\end{figure}
% walk through code of running example:
%
\cc{dblAbs} is a small procedure that doubles the absolute value of
its input and stores the result in \cc{res}.
% state the safety problem:
The program also asserts that \cc{res} is greater than or equal to $0$
before exiting.
% talk about solving Horn Clauses:
Verifying this assertion reduces to solving a recursion-free
CHC system over a set of uninterpreted predicates that represent
the control locations in \cc{dblAbs}.
%
In particular, one such system $\mcchc$ is shown in \autoref{fig:chc}.
%
%
While $\mcchc$ has been presented as the result
of a translation from \cc{dblAbs}, \sys is
purely a solver for CHC systems: it does not require access to the
concrete representation of a program, or for a given CHC system to be
the result of translation from a program at all.

@@

%% talk about expansion:
\begin{figure}[t]
  \centering
  \begin{floatrow}[2]
    \ffigbox[.45\textwidth] {%
      {\caption{$\mcchc$ as a directed hypergraph. Each relational
          predicate is depicted as a graph node while each clause is
          represented by a hyperedge. Each hyperedge is labelled by the
          fact in the corresponding CHC\@. Each node has a valid
          corresponding interpretation, written in braces.
      }\label{fig:ex-graph}}}
      {\input{fig/example}}
    \ffigbox[.45\textwidth]
      {\caption{The hierarchy of classes of recursion-free CHC
          systems. Body Disjoint and Linear systems are subsumed by
          CDD systems. Solving Directly Solvable CHC systems is in
          co-NP while solving general, recursion-free systems is
          co-NEXPTIME Complete.
      }\label{fig:hierarchy}}
      {\input{fig/hierarchy}}
  \end{floatrow}
\end{figure}
